Numerical analysis of the linear vertical shear instability in astrophysical disks

### 2014-12-29 linear_adia.tex
restructing analytic discussion

\subsubsection{Explicit solutions in the thin-disk limit}
We can construct solutions in the thin-disk limit, in which 
$\ln(\rho/\rho_0) \simeq -\zhat^2/2$. Eq. \ref{adia_iso3} becomes   
\begin{align}
  0 = \delta v_z^{\prime\prime} - \zhat A \delta v_z^\prime + \left(B
    - C \zhat^2\right)\delta v_z, \label{adia_iso4} 
\end{align}
with
\begin{align}
  &A \equiv 1 + \ii \epsilon q \hat{k},\\
  &B \equiv \hat{\sigma}^2\left(\frac{1}{\gamma} + \hat{k}^2\right) -
  \left(\frac{1}{\gamma} + \ii \hat{k} \epsilon q\right)\\
  &C \equiv \frac{\left(\gamma-1\right)}{\gamma}\hat{k}^2\left(1 - \frac{\ii
      \epsilon q}{\hat{k}}\right).\label{adia_thin}
\end{align}
Let
\begin{align}
  \delta v_z(\zhat) =
  g(\zhat)\exp\left(\frac{\alpha\zhat^2}{2}\right), \label{adia_ansatz}
\end{align}
where $\alpha$ is a constant to be chosen for convenience. Inserting
Eq. \ref{adia_ansatz} into Eq. \ref{adia_thin} gives
\begin{align}
  0 = g^{\prime\prime} - \hat{z}\left(A - 2\alpha\right)g^\prime + \left(B +
    \alpha\right)g
  +\left(\alpha^2 - \alpha A - C\right)\zhat^2 g.
\end{align}
We choose $\alpha$ to make the coefficient of $\zhat^2g$
vanish, and impose the vertical kinetic energy density
$\rho|\delta v_z|^2$ to remain finite. Then assuming $g(\zhat)$ is a
polynomial, we require  
\begin{align}
  \real\alpha < \frac{1}{2}. 
\end{align}
We therefore choose 
\begin{align}
  \alpha = \frac{1}{2}\left(A - \sqrt{A^2 + 4C}\right). 
\end{align}

@@

\subsection{Perturbations with thermal relaxation}
Having examined the extreme limits of isothermal ($t_c\to0$) and
adiabatic ($t_c\to\infty$) perturbations, we now generalize further to consider
perturbations with intermediate thermodynamic responses with general
values of $t_c$.

In this section we will pursue explicit solutions in the low-frequency,
thin-disk, nearly-Keplerian approximations as used in the development
for adiabatic solutions. The pair of ODEs for $W$ and $Q$
(Eq. \ref{ode_w}---\ref{ode_Q}) with these approximations and 
written with dimensionless variables, are
\begin{align}
  &\hat{\sigma}^2\left(Q +  \hat{k}^2W\right) \notag\\ 
  &= \hat{z} \left(1 +
    \ii\epsilon q \hat{k} \right)\left[W^\prime - \zhat \left(W -
      Q\right)\right] - \left[W^\prime - \zhat \left(W -
      Q\right)\right]^\prime\label{nearly_iso1},\\
&\beta \hat{\sigma}^2\left(W - \gamma Q\right) + \ii\hat{\sigma}
    \left(W-Q\right)\notag\\
   & = -\beta\zhat\left(\gamma-1\right) \left[W^\prime - \zhat \left(W -
      Q\right)\right]\label{nearly_iso2},
\end{align}
where we recall $\beta = t_c\Omega_k$ is the dimensionless cooling
time. It is evident that for $\beta\equiv 0$, we recover
Eq. \ref{iso_ode3}. In addition, from the expression of the vertical
velocity perturbation (Eq. \ref{lin_vz}) we have
\begin{align}
  W^\prime - \zhat \left(W -
      Q\right) = \ii\hat{\sigma}c_s\delta v_z. \label{nearly_vz}
\end{align}

\subsubsection{Perturbative effect of introducing a small but finite
  thermal relaxation time}

It is instructive to first ask the more analytically tractable question: how
do the eigenfrequencies and eigenfunctions change when we change
$t_c$ from zero to a small but finite value? For sufficiently small
$t_c$, for which the perturbations may be considered
nearly-isothermal, we expect the new solutions to only differ slighly
from the explicit isothermal solutions developed in \S\ref{iso_poly}.

%is valid for
%non-isothermal perturbations $\gamma>1$ if the thermal relaxation
%(cooling) timescale $t_c\equiv0$.

% Then we may linearize Eq. \ref{nearly_iso1}---\ref{nearly_iso2}

To determine the (assumed) small effect of introducing a short thermal
relaxation, we linearize Eq. \ref{nearly_iso1}---\ref{nearly_iso2} about a known
solution for $\beta\equiv0$. Let 
\begin{align}\label{nearly_iso_pert}
  \beta \to 0 + \delta\beta,\, W\to W+\delta W,\, Q \to Q+\delta
  Q,\,\hat{\sigma} \to \hat{\sigma} + \delta\hat{\sigma}, 
\end{align} 
where $W=Q$ is the polynomial solution described in \S\ref{iso_poly}
with $\hat{\sigma}^2$ given by Eq. \ref{sig2_iso}. Inserting
Eq. \ref{nearly_iso_pert} into
Eq. \ref{nearly_iso1}---\ref{nearly_iso2} and keeping only first order
terms, we obtain
\begin{align}
  &2\hat{\sigma}\delta\hat{\sigma}\left(1+\hat{k}^2\right)W +
  \hat{\sigma}^2 \left(\delta Q + \hat{k}^2\delta W\right)\notag\\
  &= \zhat \left(1+\ii\epsilon q \hat{k}\right)\left[\delta W^\prime -
    \zhat \left(\delta W - 
      \delta Q\right)\right] - \delta W^{\prime\prime}\notag\\
  &\phantom{=} + \left[\zhat \left(\delta W -
     \delta Q\right)\right]^\prime,\label{nearly_iso3}\\
&\ii\hat{\sigma} \left(\delta W - \delta Q\right) =
\delta\beta\left(\gamma-1\right)\left(\hat{\sigma}^2W - \hat{z}W^\prime\right).\label{nearly_iso4}
\end{align}
This is a pair of inhomogeneous ODEs with a forcing by $W$. The
homogeneous problem is, of course, just the ODE for $\beta=0$ solved
in \S\ref{iso_poly}. Hence we only seek the particular solution.

We could proceed by considering the entire set of polynomial
solutions for $W$, but it is simplest to look at the fundamental
mode. Thus we consider the `basic state' 
\begin{align*}
  W = \hat{z},\quad \hat{\sigma}^2\left(1+\hat{k}^2\right) = 1 +
  \ii\epsilon q \hat{k},
\end{align*}
then
\begin{align}
  \delta W = b \zhat^3,
\end{align}
where $b$ is a constant to be determined. Eliminating $\delta Q$ from
Eq. \ref{nearly_iso3}---\ref{nearly_iso4}, inserting the above
expressions for $W$ and $\delta W$ and balancing coefficients of
$\zhat$ and $\zhat^3$, we find
\begin{align}
 & 2\left(1+\ii\epsilon q \hat{k}\right) \delta\hat{\sigma} \notag\\& = -6b\hat{\sigma} -
2\ii \delta \beta\left(\gamma-1\right)\left(\hat{\sigma}^2-1\right) - \ii
  \hat{\sigma}^2\delta\beta\left(\gamma-1\right),\\
& 0=  2b\hat{\sigma}+\ii\delta\beta
\left(\gamma-1\right)\left(\hat{\sigma}^2 - 1\right),
\end{align}
where the expression for $\hat{\sigma}^2$ was used. Solving for
$\delta\hat{\sigma}$ gives 
\begin{align}\label{nearly_iso_dsig}
  \delta \hat{\sigma} =
  -\frac{\ii\left(\gamma-1\right)\hat{k}^2\left(\ii\epsilon
    q - \hat{k}\right)^2}{2\left(1+\ii\epsilon q \hat{k}\right)\left(1+\hat{k}^2\right)^2}\delta\beta.
\end{align}
The imaginary part of Eq. \ref{nearly_iso_dsig} is
\begin{align}
   \delta\hat{\nu} =
  -\frac{\left(\gamma-1\right)\hat{k}^2 \left(\hat{k}^2 -
      2\epsilon^2q^2\hat{k}^2 - \epsilon^2q^2\right)}{2\left(1+\epsilon^2 q^2
        \hat{k}^2\right)\left(1+\hat{k}^2\right)^2}\delta\beta.  
\end{align}
Since $\epsilon \ll 1$, introducing finite cooling $\delta\beta>0$
implies $\delta\hat{\nu} < 0$, i.e. stabilization. Interestingly, for both
$\hat{k}\to0$ and $\hat{k}\to\infty$ we find $\delta\hat{\nu}\to0$, so
stabilization by finite cooling is ineffective at very large or very
small scales. We plot Eq. \ref{nearly_iso_dsig} in Fig. \ref{domegadbeta} with
$\epsilon=0.05$, $q=-1.0$ and $\gamma=1.4$. For this disk model the
optimum wavenumber for stabilization is $\hat{k}\sim 5$---$6$.

@@

One effect of introducing finite thermal relaxation is buoyancy. % We
% show in the next section that buoyancy strongly stabilizes the
% VSI.
The solution $\delta W\propto\zhat^3$ then makes sense because it
is most significant for large $\zhat$, i.e. away from the midplane
where the effect of bouyancy first appears as $t_c$ is increased.

\subsubsection{General explicit solutions with thermal relaxation}
To develop explicit solutions of
Eq. \ref{nearly_iso1}---\ref{nearly_vz}, we eliminate variables in
favor of $\delta v_z$ to obtain
\begin{align}
  0 = \delta v_z^{\prime\prime} - z \widetilde{A}\delta v_z^\prime +
  (\widetilde{B} - \widetilde{C}\zhat^2)\delta v_z = 0,\label{nearly_iso_explicit}
\end{align}
with
\begin{align}
  &\widetilde{A} \equiv 1 + \ii \epsilon q \hat{k},\\
  &\widetilde{B} \equiv \hat{\sigma}^2\left(\chi + \hat{k}^2\right) -
  \left(\chi + \ii \epsilon q \hat{k}\right),\\
  &\widetilde{C} \equiv \left(1-\chi\right)\left(\hat{k}^2 - \ii
      \epsilon q\hat{k}\right),
\end{align}
where
\begin{align}
  \chi \equiv \frac{1-\ii\hat{\sigma}\beta}{1-\ii\hat{\sigma}\beta\gamma}.
\end{align}

The governing equation Eq. \ref{nearly_iso_explicit} has the same form
as in the adiabatic case (Eq. \ref{adia_iso4}), so we can apply the
same solution method. However, the coefficients
$\widetilde{B}$ and $\widetilde{C}$ now have a more complicated
dependence on $\hat{\sigma}$.  The adiabatic dispersion relation,
Eq. \ref{adia_disp0}, generalizes to a $6^\mathrm{th}$ order
polynomial in $\hat{\sigma}$:
\begin{align}
  0 = \sum_{l=0}^{6}c_l\hat{\sigma}^l,\label{relax_disp}
\end{align}
where the coefficients $c_l$ are given in Appendix \ref{relax_coeff}.
Eq. \ref{relax_disp} contrasts to Eq. \ref{adia_disp}, which is
quadratic in $\hat{\sigma}$ for adiabatic perturbations.

@@

%ate_theory, eps=0.05, smallq=-1d0, gmma=1.4, bmax=1.0, ncases=11, mmode=0.0, root=1, legend=[0.102,0.14,5.4,0.355], yrange=[0,6]

>>>>

\subsubsection{Explicit solutions in the thin-disk limit}\label{adia_explicit}
We can construct solutions in the thin-disk limit, in which 
$\ln(\rho/\rho_0) \simeq -\zhat^2/2$. Eq. \ref{adia_iso3} becomes   
\begin{align}
  0 = \delta v_z^{\prime\prime} - \zhat A \delta v_z^\prime + \left(B
    - C \zhat^2\right)\delta v_z, \label{adia_iso4} 
\end{align}
with
\begin{align}
  &A \equiv 1 + \ii \epsilon q \hat{k},\\
  &B \equiv \hat{\sigma}^2\left(\frac{1}{\gamma} + \hat{k}^2\right) -
  \left(\frac{1}{\gamma} + \ii \hat{k} \epsilon q\right)\\
  &C \equiv \frac{\left(\gamma-1\right)}{\gamma}\hat{k}^2\left(1 - \frac{\ii
      \epsilon q}{\hat{k}}\right).\label{adia_thin}
\end{align}
Let
\begin{align}
  \delta v_z(\zhat) =
  g(\zhat)\exp\left(\frac{\alpha\zhat^2}{2}\right), \label{adia_ansatz}
\end{align}
where $\alpha$ is a constant to be chosen for convenience. Inserting
Eq. \ref{adia_ansatz} into Eq. \ref{adia_thin} gives
\begin{align}
  0 = g^{\prime\prime} - \hat{z}\left(A - 2\alpha\right)g^\prime + \left(B +
    \alpha\right)g
  +\left(\alpha^2 - \alpha A - C\right)\zhat^2 g.
\end{align}
We choose $\alpha$ to make the coefficient of $\zhat^2g$
vanish, and impose the vertical kinetic energy density
$\rho|\delta v_z|^2$ to remain finite. Then assuming $g(\zhat)$ is a
polynomial, we require  
\begin{align}
  \real\alpha < \frac{1}{2}. 
\end{align}
We therefore choose 
\begin{align}
  \alpha = \frac{1}{2}\left(A - \sqrt{A^2 + 4C}\right). 
\end{align}

@@

\subsection{Perturbations with thermal relaxation}
Having examined the extreme limits of isothermal ($t_c\to0$) and
adiabatic ($t_c\to\infty$) perturbations, we now generalize further to consider
perturbations with intermediate thermodynamic responses with general
values of $t_c$ or $\beta$.

In this section we will pursue explicit solutions in the thin-disk
approximation. The governing equation, Eq. \ref{vertiso_gov_nondim}, is
then 
\begin{align}
  0 = \delta v_z^{\prime\prime} - z \widetilde{A}\delta v_z^\prime +
  (\widetilde{B} - \widetilde{C}\zhat^2)\delta v_z = 0,\label{nearly_iso_explicit}
\end{align}
with
\begin{align}
  &\widetilde{A} \equiv 1 + \ii \epsilon q \hat{k},\\
  &\widetilde{B} \equiv \hat{\sigma}^2\left(\chi + \hat{k}^2\right) -
  \left(\chi + \ii \epsilon q \hat{k}\right),\\
  &\widetilde{C} \equiv \left(1-\chi\right)\left(\hat{k}^2 - \ii
      \epsilon q\hat{k}\right), 
\end{align}
and $\chi =
\left(1-\ii\hat{\sigma}\beta\right)/\left(1-\ii\hat{\sigma}\beta\gamma\right)
$ in terms of dimensionless variables.

\subsubsection{The effect of introducing a small but finite
  thermal relaxation time} 
It is instructive to first ask  the more analytically tractable
question: how 
do the eigenfrequencies and eigenfunctions change when we change
$t_c$ from zero to a small but finite value? For sufficiently small
$\beta$, for which the perturbations may be considered 
nearly-isothermal, we expect the new solutions to only differ slightly
from the explicit isothermal solutions developed in \S\ref{iso_poly}.

To determine the (assumed) small effect of introducing a short thermal
relaxation, we linearize Eq. \ref{nearly_iso_explicit} about a known 
solution for $\beta\equiv0$  ($\chi\equiv 1$). 
Let 
\begin{align}\label{nearly_iso_pert}
  \beta \to 0 + \delta\beta,\, \delta v_z\to \delta v_z+\delta
  v_{z1},\,\hat{\sigma} \to \hat{\sigma} + \delta\hat{\sigma}, 
\end{align}
which implies 
\begin{align}
  \chi \to 1 + \delta\chi = 1 + \ii \hat{\sigma}\left(\gamma-1\right)\delta\beta.
\end{align}
Here $\delta v_z$ corresponds to the explicit solution developed in
\S\ref{iso_poly} with  $\hat{\sigma}^2$ given by Eq. \ref{sig2_iso}. Inserting
Eq. \ref{nearly_iso_pert} into Eq. \ref{nearly_iso_explicit}  and keeping
only first order terms, we obtain 
\begin{align}
 0 =& \delta v_{z1}^{\prime\prime} - z\left(1 + \ii\epsilon q
   k\right)\delta v_{z1}^\prime\notag\\
 &+ \left[2\hat{\sigma}\delta\hat{\sigma}\left(1 + \khat^2\right) +
   \left(\hat{\sigma}^2 - 1\right)\delta\chi \right.\notag\\
&\phantom{++} \left. + \zhat^2\left(\khat^2 -
     \ii\epsilon q \khat\right)\delta\chi\right]\delta v_z\notag\\
 &+\left[\hat{\sigma}^2\left(1 + \khat^2\right) - \left(1+\ii\epsilon
     q \khat\right)\right]\delta v_{z1}.\label{nearly_iso4}
\end{align}

We could proceed by considering the entire set of polynomial solutions
for $W$, and hence $\delta v_z$, discussed in \S\ref{iso_poly}, but it
is simplest to look at the fundamental mode. Thus we consider the `basic state' 
 \begin{align*}
   \delta v_z = 1,\quad \hat{\sigma}^2\left(1+\hat{k}^2\right) = 1 +
   \ii\epsilon q \hat{k},
 \end{align*}
 then we may seek 
 \begin{align}
   \delta v_{z1} = a \zhat^2 + b,
 \end{align}
where $a$, $b$ are constants.

Inserting the above expressions for $\delta v_z$, $\delta v_{z1}$ and
$\hat{\sigma}^2$ into Eq. \ref{nearly_iso4}, then balancing
coefficients of $\zhat^2$ and constants, we require
\begin{align}
0 &= 2a + 2\hat{\sigma}\left(1+\khat^2\right)\delta\hat{\sigma} +
\left(\hat{\sigma}^2 -1\right)\delta\chi,\notag\\
0&= 2a\left(1+\ii\epsilon q \khat\right) - \left(\khat^2 - \ii\epsilon
q \khat\right)\delta\chi.
\end{align}

Using the expressions for $\delta\chi$ and $\hat{\sigma}$ we can solve
for $\delta\hat{\sigma}$. This gives 
\begin{align}\label{nearly_iso_dsig}
  \delta \hat{\sigma} =
  -\frac{\ii\left(\gamma-1\right)\hat{k}^2\left(\ii\epsilon
      q - \hat{k}\right)^2}{2\left(1+\ii\epsilon q \hat{k}\right)\left(1+\hat{k}^2\right)^2}\delta\beta.
\end{align}
The imaginary part of Eq. \ref{nearly_iso_dsig} is
\begin{align}
  \delta\hat{\nu} =
  -\frac{\left(\gamma-1\right)\hat{k}^2 \left(\hat{k}^2 -
      2\epsilon^2q^2\hat{k}^2 - \epsilon^2q^2\right)}{2\left(1+\epsilon^2 q^2
      \hat{k}^2\right)\left(1+\hat{k}^2\right)^2}\delta\beta.  
\end{align}
Since $\epsilon \ll 1$, introducing finite cooling $\delta\beta>0$
implies $\delta\hat{\nu} < 0$, i.e. stabilization. Interestingly, for both
$\hat{k}\to0$ and $\hat{k}\to\infty$ we find $\delta\hat{\nu}\to0$, so
stabilization by finite cooling is ineffective at very large or very
small scales. We plot Eq. \ref{nearly_iso_dsig} in Fig. \ref{domegadbeta} with
$\epsilon=0.05$, $q=-1.0$ and $\gamma=1.4$. For this disk model the
optimum wavenumber for stabilization is $\hat{k}\sim 5$---$6$.

@@

One effect of introducing finite thermal relaxation is buoyancy. % We
% show in the next section that buoyancy strongly stabilizes the
% VSI.
The $\zhat^2$ depedence in $\delta v_{z1}$ then makes sense because it
is most significant for large $\zhat$, i.e. away from the midplane
where the effect of bouyancy first appears as $t_c$ is increased.

\subsubsection{General dispersion relation with thermal relaxation}\label{disp_relax}
Eq. \ref{nearly_iso_explicit} is same form
as the governing equation for the adiabatic case
(Eq. \ref{adia_iso4}). However, the coefficients $\widetilde{B}$ and $\widetilde{C}$
have a complicated dependence on $\hat{\sigma}$. 
Applying the same solution method as in \S\ref{adia_explicit}, we 
% Thus calculating the
% eigenfrequency $\hat{\sigma}$ generally requires a numerical
% approach, which we do  in \S\ref{disp_relax}. However, analytical
% results may be obtained in the limit $\beta\to0$. 
find the adiabatic dispersion relation,
Eq. \ref{adia_disp0}, generalizes to a $6^\mathrm{th}$ order
polynomial in $\hat{\sigma}$:
\begin{align}
  0 = \sum_{l=0}^{6}c_l\hat{\sigma}^l,\label{relax_disp}
\end{align}
where the coefficients $c_l$ are given in Appendix \ref{relax_coeff}.
Eq. \ref{relax_disp} contrasts to Eq. \ref{adia_disp}, which is
quadratic in $\hat{\sigma}$ for adiabatic perturbations.

@@

%ate_theory, eps=0.05, smallq=-1d0, gmma=1.4, bmax=1.0, ncases=11,
%mmode=0.0, root=1, legend=[0.102,0.14,5.4,0.355], yrange=[0,6]

% The pair of ODEs for $W$ and $Q$
% (Eq. \ref{ode_w}---\ref{ode_Q}) with these approximations and 
% written with dimensionless variables, are
% \begin{align}
%   &\hat{\sigma}^2\left(Q +  \hat{k}^2W\right) \notag\\ 
%   &= \hat{z} \left(1 +
%     \ii\epsilon q \hat{k} \right)\left[W^\prime - \zhat \left(W -
%       Q\right)\right] - \left[W^\prime - \zhat \left(W -
%       Q\right)\right]^\prime\label{nearly_iso1},\\
% &\beta \hat{\sigma}^2\left(W - \gamma Q\right) + \ii\hat{\sigma}
%     \left(W-Q\right)\notag\\
%    & = -\beta\zhat\left(\gamma-1\right) \left[W^\prime - \zhat \left(W -
%       Q\right)\right]\label{nearly_iso2},
% \end{align}
% where we recall $\beta = t_c\Omega_k$ is the dimensionless cooling
% time. It is evident that for $\beta\equiv 0$, we recover
% Eq. \ref{iso_ode3}. In addition, from the expression of the vertical
% velocity perturbation (Eq. \ref{lin_vz}) we have
% \begin{align}
%   W^\prime - \zhat \left(W -
%       Q\right) = \ii\hat{\sigma}c_s\delta v_z. \label{nearly_vz}
% \end{align}

% %is valid for
% %non-isothermal perturbations $\gamma>1$ if the thermal relaxation
% %(cooling) timescale $t_c\equiv0$.

% % Then we may linearize Eq. \ref{nearly_iso1}---\ref{nearly_iso2}

% To determine the (assumed) small effect of introducing a short thermal
% relaxation, we linearize Eq. \ref{nearly_iso1}---\ref{nearly_iso2} about a known
% solution for $\beta\equiv0$. Let 
% \begin{align}\label{nearly_iso_pert}
%   \beta \to 0 + \delta\beta,\, W\to W+\delta W,\, Q \to Q+\delta
%   Q,\,\hat{\sigma} \to \hat{\sigma} + \delta\hat{\sigma}, 
% \end{align} 
% where $W=Q$ is the polynomial solution described in \S\ref{iso_poly}
% with $\hat{\sigma}^2$ given by Eq. \ref{sig2_iso}. Inserting
% Eq. \ref{nearly_iso_pert} into
% Eq. \ref{nearly_iso1}---\ref{nearly_iso2} and keeping only first order
% terms, we obtain
% \begin{align}
%   &2\hat{\sigma}\delta\hat{\sigma}\left(1+\hat{k}^2\right)W +
%   \hat{\sigma}^2 \left(\delta Q + \hat{k}^2\delta W\right)\notag\\
%   &= \zhat \left(1+\ii\epsilon q \hat{k}\right)\left[\delta W^\prime -
%     \zhat \left(\delta W - 
%       \delta Q\right)\right] - \delta W^{\prime\prime}\notag\\
%   &\phantom{=} + \left[\zhat \left(\delta W -
%      \delta Q\right)\right]^\prime,\label{nearly_iso3}\\
% &\ii\hat{\sigma} \left(\delta W - \delta Q\right) =
% \delta\beta\left(\gamma-1\right)\left(\hat{\sigma}^2W - \hat{z}W^\prime\right).\label{nearly_iso4}
% \end{align}
% This is a pair of inhomogeneous ODEs with a forcing by $W$. The
% homogeneous problem is, of course, just the ODE for $\beta=0$ solved
% in \S\ref{iso_poly}. Hence we only seek the particular solution.

% We could proceed by considering the entire set of polynomial
% solutions for $W$, but it is simplest to look at the fundamental
% mode. Thus we consider the `basic state' 
% \begin{align*}
%   W = \hat{z},\quad \hat{\sigma}^2\left(1+\hat{k}^2\right) = 1 +
%   \ii\epsilon q \hat{k},
% \end{align*}
% then
% \begin{align}
%   \delta W = b \zhat^3,
% \end{align}
% where $b$ is a constant to be determined. Eliminating $\delta Q$ from
% Eq. \ref{nearly_iso3}---\ref{nearly_iso4}, inserting the above
% expressions for $W$ and $\delta W$ and balancing coefficients of
% $\zhat$ and $\zhat^3$, we find
% \begin{align}
%  & 2\left(1+\ii\epsilon q \hat{k}\right) \delta\hat{\sigma} \notag\\& = -6b\hat{\sigma} -
% 2\ii \delta \beta\left(\gamma-1\right)\left(\hat{\sigma}^2-1\right) - \ii
%   \hat{\sigma}^2\delta\beta\left(\gamma-1\right),\\
% & 0=  2b\hat{\sigma}+\ii\delta\beta
% \left(\gamma-1\right)\left(\hat{\sigma}^2 - 1\right),
% \end{align}
% where the expression for $\hat{\sigma}^2$ was used.
